---
title: DANL 200 Project
subtitle: "Data-Driven Mastery: Unlocking Business Potential"
author: 
  - Taylor Johnson

toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

from: markdown+emoji
---
```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )

all_seasons = read.csv("all_seasons.csv")

d2 <- all_seasons[!all_seasons$Team.SR.avg <= 0 & !all_seasons$Team.SR.avg == 'P' & !all_seasons$Enemy.SR.avg == 'P',]

d2 <- transform(d2, Team.SR.avg = as.numeric(Team.SR.avg),
                Enemy.SR.avg = as.numeric(Enemy.SR.avg))

d2 <- d2 %>%
  select(season,Team.SR.avg,Enemy.SR.avg,Result) %>%
  mutate(SR.Diff = Enemy.SR.avg - Team.SR.avg)

SRDiffResult <- d2

SRDiffResult$SR.Diff <- ifelse(d2$SR.Diff < 0, 'advantage', "disadvantage")

SRDiffResult <- SRDiffResult %>%
  group_by(season,SR.Diff) %>%
  mutate( total_matches = n())

d3 <- all_seasons[!all_seasons$End.SR == 'P',]

d3 <- transform(d3,End.SR = as.numeric(End.SR))

WLDLeaver <- all_seasons[!all_seasons$Leaver == "No" & !all_seasons$Leaver == "",] %>%
  group_by(season,Leaver) %>%
  mutate( Total_leaver = n() )


```



# Introduction

This Project is an exploration of an individual's performance during four seasons of the competitive FPS game Overwatch.


# Data

The data.frame `all.seasons` consists of an individual's personal competitive ranked data that he manually recorded while playing seasons 3, 4, 9, and 10 of the FPS game Overwatch. Season 3 appears to have missing information, but we can attribute this to the fact that additional metrics were introduced in later seasons. The data provided is comprehensive, consisting of all of the data that is shown to the player during and after each match.

## Summary Statistics

```{r}
all_seasons <- all_seasons
```

```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(all_seasons) 
```


```{r}
skim(all_seasons) %>% 
  select(-n_missing)
```

## W/L/D versus Player Left Match
The following shows the percentage of matches the individual either won, lost, or drew depending on if a player left his team or the enemy team. 

```{r}
WLDLeaver <- WLDLeaver %>%
  group_by(season,Leaver,Result,Total_leaver) %>%
  count() %>%
  summarize(Prop = n / Total_leaver * 100) %>%
  select(season,Leaver,Result,Prop)
```

```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(WLDLeaver) 
```

## W/L/D versus Team SR Differential
The following shows the percentage of games this individual either won, lost, or drew per season given that his team had a higher skill rating than the enemy team (advantage) or that his team had a lower skill rating than the enemy team (disadvantage).

```{r}
SRDiffResult <- SRDiffResult %>%
  group_by(season,SR.Diff,Result,total_matches) %>%
  count() %>%
  summarize( Prop = round( n / total_matches * 100, digits = 1) ) %>%
  select(season,SR.Diff,Result,Prop)
```

```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(SRDiffResult) 
```

## Skill Fluctuation Per Season
The following is a visualization of the fluctuation of this individual's Skill Ranking (SR) after each match for each of the four seasons data is available.


```{r}

ggplot(data = d3) +
  geom_point(mapping = aes(x = Game..,y = End.SR,)) +
  xlab('Match Number') +
  ylab('Skill Rating') +
  facet_wrap(.~season)

ggplot(data = d3) +
  geom_point(mapping = aes(x = Game..,y = End.SR,color = season)) +
  xlab('Match Number') +
  ylab('Skill Rating') 
 
```


